Speed estimation for vehicles using \\SVM classification and edge detection

### 2016-06-15 Administratie/report/paper.tex
update report

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{subcaption}
\captionsetup{compatibility=false}

\usepackage{url}   
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

\begin{abstract}
This is the abstract: TODO
\keywords{SVM classification, Local Binary Patterns, edge detection}
\end{abstract}

\section{Introduction}
The goal of this paper is to determine a maximum speed for a moving vehicle using only camera images and information from the steering column.

@@

A additional feature that can be realized using the electronics that are already available in some cars, is automated maximum speed detection. This speed detection would simulate the braking distance towards the nearest obstacle and inform the user. There are various ways to achieve this. Commonly used systems in adaptive cruise control are lidar and radar.  The choice of sensor presents classic design trade-offs \cite{Jones2001}.  Lidar  is  less  expensive  to  produce  and  easier  to package  but  performs  poorly  in  rain  and  snow. Another problem is that accumulations of mud, dust or snow on the car can block lidar beams. Radar-based  systems,  on  the  other  hand,  can ''see'' at least 150 meters ahead in fog or rain heavy enough to cut the driver’s ability to see down to 10  meters  or  less.

Because of the problems with both these systems, we propose to use a detection system based on camera images. These images present a few advantages over a system using lidar or radar. First of all cameras are way cheaper to install. On top of that they see color and are able to gain very high resolution for more distant objects. There are several downsides to using cameras. They require light to work properly, which becomes a problem for example at night. Secondly computer vision systems using camera images can use a lot of CPU power. Nonetheless cameras provide a cheap and accessible platform for immediate applications in real-world scenarios.

Section 2 discusses some relevant background information mostly concerning Local Binary Patterns and SVM classification. Section 3 describes the methods used in order to achieve the best results. The results are then discussed in section 4. In the last section an overview of the most important results is presented.

@@

\begin{figure}[h]
\centering
\includegraphics[height=7cm]{fig/SVM_hyperplane.png}
\caption{Choosing the hyperplane that maximizes the margin.}
\label{fig:hyperplane}
\end{figure}

@@

\subsection{Precision, recall, F-scores}
TODO: Bjorn

@@

\begin{figure}[ht]
\centering
\begin{subfigure}{.49\textwidth}
  \centering
  \includegraphics[width=1\textwidth]{fig/svm_prediction_16_lbp_marks.png}
  \caption{Block size 16x16px}
\end{subfigure}
\begin{subfigure}{.49\textwidth}
  \centering
  \includegraphics[width=1\textwidth]{fig/svm_prediction_32_lbp_marks.png}
  \caption{Block size 32x32px}
\end{subfigure}
\caption{SVM prediction using only LBP values and including road marks. Green blocks were predicted to be road, red to be non-road.}
\label{fig:methods-block-sizes}
\end{figure}

>>>>

\documentclass[runningheads,a4paper]{llncs}
\usepackage[english]{babel}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{booktabs}
\usepackage{float}

\usepackage{url}   
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\newcommand\fnumber{\mathop{\mbox{$F$-$score$}}}
\noindent\keywordname\enspace\ignorespaces#1}

@@

\begin{abstract}
This is the abstract: The goal of this paper it to determine the maximum speed for a moving vehicle in traffic, using only camera images and information from the steering column. We construct a system that combines SVM classification and edge detection to foresee possible obstacles on the given trajectory of the car. The maximum speed is computed so that braking in time will avoid collision with those obstacles. 
TODO: hoe goed is dit systeem?
\keywords{SVM classification, Local Binary Patterns, edge detection}
\end{abstract}

\section{Introduction}
This paper determines the maximum speed for a moving vehicle in traffic, using only camera images and information from the steering column. We construct a system that combines SVM classification and edge detection to foresee possible obstacles on the given trajectory. The maximum speed is computed so that braking in time will avoid collision with those obstacles.

@@

An additional feature that can be realized using the electronics that are already available in these cars, is automated maximum speed detection. This speed detection would simulate the braking distance towards the nearest obstacle and inform the user. There are various ways to achieve this. Commonly used sensors in adaptive cruise control are lidar and radar.  The choice of sensor presents classic design trade-offs \cite{Jones2001}.  Lidar  is  less  expensive  to  produce  and  easier  to package  but  performs  poorly  in  rain  and  snow. Another problem is that accumulations of mud, dust or snow on the car can block lidar beams. Radar-based  systems,  on  the  other  hand,  can ''see'' at least 150 meters ahead in fog or rain heavy enough to cut the driver's ability to see down to 10 meters or less.

Because of the problems with both these systems, this paper proposes the use of a detection system based on camera images. These images present some advantages over a system using lidar or radar. First of all cameras are way cheaper to install. On top of that they see color and are able to gain very high resolution for more distant objects. There are several downsides to using cameras. They require light to work properly, which becomes a problem for example at night. Secondly computer vision systems using camera images can use a lot of CPU power. Nonetheless cameras provide a cheap and accessible platform for immediate applications in real-world scenarios. On top of that, cameras could be used in combination with lidar and radar to provide even better results.

\subsection{Overview}
Section 2 discusses some relevant background information mostly concerning Local Binary Patterns and SVM classification. Section 3 describes the methods used in order to achieve the best results. The results are then discussed in section 4. In the last section, an overview of the most important results is presented.

@@

\begin{figure}[H]
\centering
\includegraphics[height=7cm]{fig/SVM_hyperplane.png}
\caption{Choosing the hyperplane that maximizes the margin.}
\label{fig:hyperplane}
\end{figure}

@@

@@

\begin{figure}[h]
\centering
\begin{subfigure}{.49\textwidth}
  \centering
  \includegraphics[width=1\textwidth]{fig/svm_prediction_16_lbp_marks.png}
  \caption{Block size 16x16px}
\end{subfigure}
\begin{subfigure}{.49\textwidth}
  \centering
  \includegraphics[width=1\textwidth]{fig/svm_prediction_32_lbp_marks.png}
  \caption{Block size 32x32px}
\end{subfigure}
\caption{SVM prediction using only LBP values and including road marks. Green blocks were predicted to be road, red to be non-road.}
\label{fig:methods-block-sizes}
\end{figure}
